Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/survey.tex
small changes here and there.

Table \ref{tab:compare} shows that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object). However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement.

RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
A controlled analysis of the effect of context on choice in naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories. Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the set of categories in MSCOCO included is quite small ($80$~COCO categories).
To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming at a large scale.

@@

% gbt: I'm commenting out this analysis because it is not really relevant for assessing how useful RefCOCO is to study object naming: what it shows is that names appear at many different levels of a taxonomy, although they tend to be concentrated in middle levels (especially 6-7; in agreement with basic level hypothesis). To me, this is a data result, not a dataset result (clear?). 
% \paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
% We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
% We estimate this distance as the minimal path length of all synsets of a word  to the root node.
% Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
% We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
% Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
% At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).

@@

This dataset has three main differences with respect to \refcoco/+: (i) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (ii) the images and the production of entity mentions were not subject to any constraints; (iii) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}). %\gbt{Any idea what kind of categories are covered in \flickr?}
Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
The number of annotations per object, $2.3$\ annotations, is comparable to \refcoco.
This dataset is suitable to analyze object naming in descriptions, for a quite large set of categories (although, again, not enough annotations are available to analyze image-specific naming data).

@@

\vgenome (VG, \newcite{krishna2016visualgenome}) is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
%\paragraph{Collection and annotation procedure}
\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
The data collection followed a complex procedure, involving many different rounds of annotation.
The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).

@@

Some of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.

However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

Table \ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). 
We think that this might be an effect of our category selection procedure explained in Section \ref{sec:data}. However, interestingly, the portion of objects that have different names associated with them is still extremely small.
Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).

@@

While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is. The RefCOCO data (and to some extent the Flickr30k data) suggests that for most objects there is more than one available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all. 
The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.

>>>>

Table~\ref{tab:compare} shows that the multiple annotations ($2.8$~on average) actually contain a considerable amount of variation in naming (almost~$2$ different names on average per object). 
%However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement. 
However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement. \cs{double-check formulation}

RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
A controlled analysis of the effect of context on choice in naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories. Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
Also, while in \refcoco the elicited names can be assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
Finally, the underlying set of MS COCO categories is quite small ($80$~categories).
To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming at a large scale.

@@

% gbt: I'm commenting out this analysis because it is not really relevant for assessing how useful RefCOCO is to study object naming: what it shows is that names appear at many different levels of a taxonomy, although they tend to be concentrated in middle levels (especially 6-7; in agreement with basic level hypothesis). To me, this is a data result, not a dataset result (clear?). 
% \paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
% We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
% We estimate this distance as the minimal path length of all synsets of a word  to the root node.
% Table~\ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
% We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
% Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
% At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).

@@

This dataset has three main differences with respect to \refcoco/+: (i) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (ii) the images and the production of entity mentions were not subject to any constraints; (iii) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table~\ref{tab:compare}). %\gbt{Any idea what kind of categories are covered in \flickr?}
Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
The number of annotations per object, $2.3$\ annotations, is comparable to \refcoco.
This dataset is suitable to analyze object naming in descriptions, for a quite large set of categories (although, again, not enough annotations are available to analyze image-specific naming data).

@@

\vgenome (VG, \newcite{krishna2016visualgenome}) is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
%\paragraph{Collection and annotation procedure}
\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
The data collection followed a complex procedure, involving many different rounds of annotation.
The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure~\ref{fig:bird}).

@@

Some of the main advantages of \vg are its size, with $3.8$~million objects ($108$K images) as opposed to $50$K and $243$K for the other two datasets, and its category coverage, with a vocabulary of object names of $105$K compared to $5$K/$10$K.
Another plus is the fact that it in principle provides exhaustive annotations of objects in an image, often with several region descriptions and possibly object names per object.
This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.

However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
%This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
%For instance, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Finally, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
Hence, the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($5$\%) seem to be an effect of this partial linking problem.
We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.,~truly overlapping objects).

Table~\ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of $7$~annotations per object. 
We think that this might be an effect of our category selection procedure explained in Section~\ref{sec:data}. However, interestingly, the portion of objects that have different names associated with them is still extremely small.
Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names ($70$\%).

@@

While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is. The RefCOCO data (and to some extent the Flickr30k data) suggests that for most objects there is more than one available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all. 
The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
This shows that to be able to analyze object naming in more detail, it is crucial to have naming data from many subjects for the same objects. 
Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
